% File: intro.tex
% Date: Wed Jun 17 21:45:19 2015 +0800
% Author: Yuxin Wu <ppwwyyxxc@gmail.com>
\section{Introduction}
\subsection{Compilation}
Dependencies:

\begin{enumerate}
    \item gcc $ \ge$ 4.7
    \item Eigen\footnote{\url{http://eigen.tuxfamily.org}}
    \item CImg\footnote{\url{http://cimg.eu}} (already included in the repository)
    \end{enumerate}
    CImg is only used to read and write images, and it optionally depends
    on libpng, libjpeg.

Compilation:
\begin{lstlisting}
$ cd src && make
\end{lstlisting}

\subsection{Run}
Various parameters are saved in \verb|src/config.cfg|.
Here I'm introducing some of them.

Four modes of stitching are available (set/unset the options in config file)
\begin{description}
  \item[cylinder mode] When the following conditions meet, this mode usually yields better results:
\begin{itemize}
  \item Images are taken with almost-pure rotation. (as common panoramas)
  \item Images are given in the left-to-right order. (I might fix this in the future)
  \item Images are taken with the same camera, and a good \verb|FOCAL_LENGTH| is set.
\end{itemize}

\item[camera estimation mode] No translation is the only requirement.
  It can usually work well as long as you don't have too few images.
  But it's slower because it needs to perform pairwise matches.

\item[translation mode] Simply stitch images together by affine transformation.
  It works when camera performs pure translation.  It also requires ordered input.

\item[naive mode] Just stitch images together by homography and all done. Not very useful.
\end{description}

The first two modes are complex and they will be introduced in \secref{cylinder}
and \secref{camera_estimate}.


Some other options users may care:
\begin{itemize}
    \item \verb|FOCAL_LENGTH|: focal length of your camera in
      35mm equivalent\footnote{\url{https://en.wikipedia.org/wiki/35_mm_equivalent_focal_length}}. Only used in cylinder mode.
    \item \verb|STRAIGHTEN|: Only used in camera estimation mode. Whether to try straighten the result. Good to set when dealing with rotational panorama.
    \item \verb|CROP|: whether to crop the final image to avoid black border.
\end{itemize}
% TODO see xxx for details

Other parameters are quality-related.
The default values are generally good for images with more than 0.7 megapixels.
If your images are too small and cannot give satisfactory results,
it might be better to resize your images rather than tune the parameters.

To run the stitcher, use
\begin{lstlisting}
./image-stitching <file1> <file2> <file3> ...
\end{lstlisting}

Output file is \verb|out.png|.


In cylinder and translation mode, the input file names need to have the correct order.

