%File: transform.tex
%Author: Yuxin Wu <ppwwyyxx@gmail.com>

\subsection{Transformation}
\label{sec:transform}

For any two images taken from a camera at some fixed point,
they can be related by a homography matrix $H$,
such that for a pair of corresponding point $ p=(x,y,1), q = (u,v,1)$,
we have
\[ p \sim Hq\]
The homogrpahy matrix has the following two fomulations:
\begin{enumerate}
  \item Homography I: $H = \begin{bmatrix} a_{11} &a_{12} & a_{13}\\ a_{21} & a_{22} & a_{23}\\ a_{31} & a_{32} & 1\end{bmatrix}$

  \item Homography II:
    $H = \begin{bmatrix} a_{11} &a_{12} & a_{13}\\ a_{21} & a_{22} & a_{23}\\ a_{31} & a_{32} & a_{33}\end{bmatrix} $
    and $\begin{Vmatrix} H \end{Vmatrix} = 1$
\end{enumerate}

When two images are taken with only camera translation
and rotation aligned with the image plane (no skew),
then they can be related by an affine matrix of the following form:
\[ A = \begin{bmatrix} a_{11} &a_{12} & a_{13}\\ a_{21} & a_{22} & a_{23}\\ 0 & 0 & 1\end{bmatrix} \]

% TODO solve
\textbf{RANSAC} (Random Sample Consensus) algorithm\cite{ransac} is used to calculate a transformation matrix.
In every iteration, several matched pairs is randomly chosen to calculate a best-fit transformation matrix,
and the pairs which agree with the matrix are taken as inliers. It's implemented in \verb|stitch/transform_estimate.cc|.

Given a set of matches, affine and the first kind of homography transformation can be solved
by least-squares fitting an over-determined linear system.
The second kind of homography transformation can be solved by finding eigenvectors.
These estimation are implemented in \verb|lib/imgproc.cc|.

After each matrix estimation, I performed
a ``health check`` to the matrix,
to avoid mal-formed transformation
estimated from false matches.
This includes two checks: (see \verb|stitch/transform.hh|)
\begin{enumerate}

  \item  The skew factor in homography
    ($ H_{3,1},H_{3,2}$) cannot be too large. Their
    absolute values are usually less than 0.002.

  \item Flipping cannot happen in image stitching.
    A homography is rejected if it flips either $x$
    or $y$ coordinate.
\end{enumerate}

For a matched pair of images,
a confidence for this match
is assigned by taking the ratio of inliers
among all the feature matches. This is
suggested by \cite{panoramic-sift}, and is useful
in the construction of global structure.
